Corotating Clumps Around Adolescent Low-Mass Stars: Four Years of TESS

### 2023-07-08 paper/ms.tex
update ms

% 250 word max!
\begin{abstract}
  Complex quasiperiodic variables (CQVs) are low-mass
  pre-main-sequence stars with nearly periodic optical modulation.
  The modulation is likely induced by dust or gas clumps in orbit at
  the Keplerian corotation radius.  Here, we report new CQVs
  discovered in TESS data collected between July~2018 and Sep~2022.
  Our search of \nstarssearched\ K- and M-dwarfs with $T$$<$16 and
  $d$$<$150\,pc yielded \ngoods\ gold-standard CQVs.  Most of these
  discoveries are new, and they include the brightest and closest
  examples of this class of object known ($T$$\approx$9.5;
  $d$$\approx$20\,pc), as well as the most massive
  ($\approx$0.65\,M$_\odot$).  A few objects are outliers among
  outliers; LP 12-502 for instance shows a ``dip complex'' with a
  period and total duration that are fixed over more than 1{,}000
  cycles, but which in detail exhibits anywhere from four to eight
  local minima per cycle.  LP-502 also displayed distinct superposed
  periods simultaneously, and displayed drastic shape changes shortly
  after flares.  Broadly speaking, we find that none of the CQVs
  maintain a fixed light curve shape over timescales of more than a
  few hundred cycles, and we revisit the arguments for why transient
  corotating material is the most viable explanation.  In the future,
  we expect that our sample will facilitate modeling and observational
  efforts aimed at understanding these objects, and connecting them to
  the broader contexts of star, disk, and exoplanet evolution.  For
  instance, if the transiting material is dust, then the rate of dip
  evolution implies that of order an asteroid belt's worth of mass
  passes through these structures over the $10^8$ years for which they
  are observed.
\end{abstract}

@@

		\vspace{-0.6cm}
		\subfloat{
			\includegraphics[width=0.8\textwidth]{f1b.pdf}
		}
	\end{center}
		\vspace{-0.3cm}
	\caption{
		{\bf Complex quasiperiodic variables (CQVs)}:
		{\it Top:} Phase-folded TESS light curves of three CQVs.  Each is
		stacked over one month.  Gray are raw 2-minute data; black bins to
		300 points per cycle.  Periods in hours are in the bottom right of
		each panel.  Left-to-right, the objects are LP 12-502
		(TIC 402980664; Sector~19), TIC 94088626 (Sector 10), and TIC
		425933644 (Sector~28).
		{\it Bottom:} Cartoon models for the phenomenon.  The dust clump
		scenario
		(lower left) and prominence scenario (lower center) both invoke centrifugally-supported material at the
		corotation radius.
		We disfavor the screen scenario (see Section~\ref{sec:intro}).
	}
	\label{fig:f1}
\end{figure*}

@@

\begin{figure*}[!tp]
	\begin{center}
		\centering
		\includegraphics[width=\textwidth]{f2.pdf}
    \vspace{-0.7cm}
		\caption{
      {\bf CQVs found in the TESS 2-minute data.}
      Phased TESS light curves over one month are shown for \ngoods\
      CQVs.  Gray are raw 2-minute data; black bins to 300 points per
      cycle.  Each panel is labeled by the TIC identifier, the TESS
      sector number, and the period in hours.  Objects are ordered
      such that sources with the most TESS data available are on top
      (see Section~\ref{sec:catalog}).
		}
		\label{fig:cqvs}
	\end{center}
\end{figure*}

@@

Figure~\ref{fig:evoln} shows ``before'' and ``after'' views of 27 CQVs
for which TESS 120-second cadence observations were available at least
two years apart.  Such a baseline was available for 32 of the
confirmed \ngoods\ CQVs in our catalog; for plotting purposes we show
the brightest 27.  Of these 27 CQVs, a few show clear signs of the
phenomenon in one sector, and marginal or non-existence signs in the
other.  While there is some subjectivity in this assessment, to our
eyes cases for which at least one sector would be flagged as
``ambiguous'' include
TIC~368129164 (Sector 23 might be labeled an EB),
TIC~177309964 (Sector 38 would be simply a rotating star),
TIC~404144841 (Sector 38 looks like a rotating star),
TIC~201898222 (Sector 3 looks like a rotating star),
TIC~144486786 (Sector 32 might be an RS CVn),
and
TIC~38820496 (Sector 28 might be an RS CVn).
TIC~193831684, assessed on a single-sector basis, would probably be
labeled an eclipsing binary---in fact, \citet{2021ApJ...912..123J}
implicitly have already given this source such a label.  However,
based on the the shape evolution between Sectors 13 and 39, it is a
CQV.  One could easily also imagine in cases like TIC~206544316 that
if observed at lower signal to noise, the drastic shape evolution
would not be appreciated.  We emphasize that the periods themselves
were all stable to $<$0.1\%.  Broadly speaking, this shape evolution
suggests that CQVs have an ``on/off'' duty cycle of $\approx$75\%.
This type of correction is likely worth including in population-level
estimates of how intrinsically common CQVs are in the low-mass stellar
population \citep[e.g.][]{2022AJ....163..144G}.

\begin{figure*}[!tp]
	\begin{center}
		\centering
		\includegraphics[width=\textwidth]{f3.pdf}
		\vspace{-0.6cm}
		\caption{
		{\bf CQVs keep their periods but change their shapes.}
      32 of our \ngoods\ CQVs from Figure~\ref{fig:cqvs} had
      120-second cadence TESS data available for a baseline of at
      least two years; the 27 brightest are shown here.  Each panel
      shows one sector of TESS data, and is phased to its deepest
      minimum in flux.  Each panel's title shows the TIC identifier
      and approximate period in hours.  Text insets show the TESS
      sector numbers, which generally span two years, or at least
      1{,}000 cycles.  The vertical scale is fixed across sectors to
      clarify shape changes.
		}
		\label{fig:evoln}
	\end{center}
\end{figure*}

@@

\begin{figure*}[!tp]
	\begin{center}
		\centering
		\includegraphics[width=\textwidth]{f4.pdf}
		\vspace{-0.4cm}
		\caption{
      {\bf LP 12-502 (TIC~402980664) light curve}, where each time
      chunk represents one TESS orbit.  Data were acquired in Sectors
      18-19, 25-26, 53, and 57-58.  Flares are drawn in gray.  The red
      vertical lines highlight apparently instantaneous state changes
      in the shape of the dip pattern.  The light curve is binned to
      15-minute intervals so that there are 96 points per day.  Data
      gaps with more than one missing 15-minute cadence appear in
      white.
		}
		\label{fig:lplc}
	\end{center}
\end{figure*}

\begin{figure*}[!t]
	\begin{center}
		\centering
		\includegraphics[width=\textwidth]{f5.pdf}
		\vspace{-0.45cm}
		\caption{
      {\bf Evolution of LP 12-502} ($P$=18.6\,h) at fixed period and
      epoch over three years.  Each panel shows one (stacked) TESS
      orbit; small text denotes relative cycle number.  There are 200
      binned black points per cycle.  The TESS pointing law dictates
      time gaps; larger gaps tend to yield larger shape changes.  The
      dips usually evolve over tens to hundreds of cycles.  However
      cycles 1233-1264 show a dip that ``switched'' from a depth and
      duration of 3\% and 3\,hr to 0.3\% and 1\,hr over less than one
      cycle (cf.~Figure~\ref{fig:lplc}).
		}
		\label{fig:lp}
	\end{center}
\end{figure*}

@@

\subsection{Mass flux estimate}

@@

In this work, we analyzed TESS 120-second cadence data collected
between July~2018 and Sep~2022, and searched it for complex
quasiperiodic variables (CQVs).  Our search sample included
\nstarssearched\ K- and M-dwarfs within 150\,pc, and was $\gtrsim
80\%$ complete within 30\,pc, and $\lesssim 10\%$ complete at
distances exceeding 100\,pc.

@@

Analyzing the CQV light curves, we draw the following conclusions.

\begin{enumerate}
	%
  \item CQVs are {\it quasi}periodic.  While the mean periods in our
    sample seem to remain fixed over the span of available
    observations, the light curve shapes themselves evolve, similar to
    rotating stars.
	%
  \item The same CQV can show dips with similar but clearly
    distinct periods.  LP 12-502, for instance, showed dips with four
    distinct periods within $\pm 0.3\%$ of its fundamental period,
    sometimes simultaneously, and each lasting for up to 50 cycles.
  	%
    \item CQVs evolve over timescales that are both secular
    ($>$100\,cycles) and impulsive ($<$1 cycle).  ``State-switches''
    can cause dips to collapse instantaneously, and are often (but not
    exclusively) linked with observed optical flares.  Dip growth
    however seems to happen over durations of at least ten cycles, and
    slow dip decay also happens.
    %
    \item The rate of dip evolution can be used to place a model-dependent
    constraint on amount of material that is either being accreted or ejected
    during the state changes.
    Order of magnitude estimates require at least an asteroid belt's worth
    of dust ($10^{-4}$\,$M_\oplus$) over $10^8$ years, or a factor of 100
    larger if the material is gas.
    %
  \item The CQV phenomenon persists for at least 150\,Myr, based on
    the existence of multiple CQVs in AB Dor, the Pleiades, and
    Psc-Eri.  It may extend to even older ages, however the lack of
    detected CQVs in the Hyades and Praesepe suggests that the
    lifetime of the phenomenon may be limited to the first few hundred
    million years.
	%
  \item The duty cycle for CQVs seems to be $\approx 75$\%, based on
    the fraction of bonafide CQVs that turned on or turned off during
    TESS re-observations, two years after their initial observation.
  %
  \item Observed CQVs span a stellar mass range of 0.1-0.8\,M$_\odot$ (Section~\ref{subsec:extreme}).
\end{enumerate}

Many questions remain.  Is the eclipsing material responsible for the
phenomenon gas, or dust?  After correcting for line-of-sight
inclination, do most M-dwarfs go through a phase of trapping material
a few stellar radii away from their surfaces?  What observational
signatures distinguish the proposed models?
What physically sets the extremes of the
CQV population, such as the longest rotation periods, hottest stellar
temperatures, and oldest stellar ages?  And finally, what connections,
if any, do CQVs have to topics such as stellar evolution, M-dwarf
magnetic fields, debris disks, and close-in exoplanets?  
Additional theoretical work could help in resolving many of these questions,
and would contain rich puzzles in plasma physics, MHD, and radiative transfer, in
addition to the dynamos of young, fully-convective stars.

On the observational front, expanding our analysis of the TESS data to the full frame images
could yield a truly volume-limited selection function, and would
expand the CQV census within 50\,pc by about a factor of two.
Out to larger volume (e.g.~200\,pc), the yield boost would be more
than an order of magnitude.
While such studies would be important for improving our understanding
of CQV population demographics,
independent programs aimed at acquiring
mid- and high-resolution time-series spectroscopy hold the best chance
at detecting
either gas or dust absorption signatures over the span of any
given CQV cycle.
The challenges intrinsic to such observations seem worth the effort.

\acknowledgments
This work was supported by the 
Heising-Simons 51~Pegasi~b Fellowship (LGB).
TIC 402980664 was observed at 120-second cadence thanks to the TESS Guest
Investigator programs G022252 (PI: J.~Schlieder; Sectors 18, 19, 25,
26) and G04168 (PI: R.~Jayaraman; Sector 53).

{\bf DRAFT AUTHOR CONTRIBUTION STATEMENTS -- PLEASE REVISE IF 
	APPROPRIATE)}
LGB~and RJ conceived the project and executed the
dip-based and Fourier-based searches, respectively.
LGB~drafted the initial manuscript, and performed the cluster
membership, SED, and variability analyses.
SR and RJ vetted the results from the Fourier search.
LAH advised on project scope and experiment design.
GAB acquired and maintained the servers used to run the dip-finding
pipeline.
GRR is an architect of the TESS mission.
All authors assisted in manuscript revision.

>>>>

% 250 word max!
\begin{abstract}
  Complex quasiperiodic variables (CQVs) are low-mass
  pre-main-sequence stars with nearly periodic optical modulation.
  The modulation is likely induced by dust or gas clumps in orbit at
  the Keplerian corotation radius.  Here, we report new CQVs
  discovered in TESS data collected between July~2018 and Sep~2022.
  Our search of \nstarssearched\ K- and M-dwarfs with $T$$<$16 and
  $d$$<$150\,pc yielded \ngoods\ gold-standard CQVs.  Most of these
  discoveries are new, and they include the brightest
  ($T$$\approx$9.5) and closest ($d$$\approx$20\,pc)
  examples of this class of object known, as well as the most massive
  ($\approx$0.65\,M$_\odot$).  A few objects are outliers among
  outliers; LP 12-502 for instance shows a ``dip complex'' with a
  period and total duration that are fixed over more than 1{,}000
  cycles, but which in detail exhibits anywhere from four to eight
  local minima per cycle.  LP-502 also displayed distinct superposed
  periods simultaneously, and displayed drastic shape changes shortly
  after flares.  Broadly speaking, we find that none of the CQVs
  maintain a fixed light curve shape over timescales of more than a
  few hundred cycles, and we revisit the arguments for why transient
  corotating material is the most viable explanation.  In the future,
  we expect that our sample will facilitate modeling and observational
  efforts aimed at understanding these objects, and connecting them to
  the broader contexts of star, disk, and exoplanet evolution.  For
  instance, if the transiting material is dust, then the rate of dip
  evolution implies that of order an asteroid belt's worth of mass
  passes through these structures over the $10^8$ years for which they
  are observed.
\end{abstract}

@@

		\vspace{-0.6cm}
		\subfloat{
			\includegraphics[width=0.8\textwidth]{f1b.pdf}
		}
	\end{center}
		\vspace{-0.3cm}
	\caption{
		{\bf Complex quasiperiodic variables (CQVs)}:
		{\it Top:} Phase-folded TESS light curves of three CQVs.  Each is
		stacked over one month.  Gray circles are raw 2-minute data; black
    circles bin to
		300 points per cycle.  Periods in hours are in the bottom right of
		each panel.  Left-to-right, the objects are LP 12-502
		(TIC 402980664; Sector~19), TIC 94088626 (Sector 10), and TIC
		425933644 (Sector~28).
		{\it Bottom:} Cartoon models for the phenomenon.  The dust clump
		scenario
		(lower left) and prominence scenario (lower center) both invoke centrifugally-supported material at the
		corotation radius.
		We disfavor the screen scenario (see Section~\ref{sec:intro}).
	}
	\label{fig:f1}
\end{figure*}

@@

\begin{figure*}[!tp]
	\begin{center}
		\centering
		\includegraphics[width=0.98\textwidth]{f2.pdf}
    \vspace{-0.3cm}
		\caption{
      {\bf CQVs found in the TESS 2-minute data.}
      Phased TESS light curves over one month are shown for \ngoods\
      CQVs.  Gray are raw 2-minute data; black bins to 300 points per
      cycle.  Each panel is labeled by the TIC identifier, the TESS
      sector number, and the period in hours.  Objects are ordered
      such that sources with the most TESS data available are on top
      (see Section~\ref{sec:catalog}).
		}
		\label{fig:cqvs}
	\end{center}
\end{figure*}

@@

Figure~\ref{fig:evoln} shows ``before'' and ``after'' views of 27 CQVs
for which TESS 120-second cadence observations were available at least
two years apart.  Such a baseline was available for 32 of the
confirmed \ngoods\ CQVs in our catalog; for plotting purposes we show
the brightest 27.  
We have phased each sector to its own local minimum because for most of the
sources we do not know the period at the precision necessary to be able to
accurately propagate it over two years.

Of these 27 CQVs in Figure~\ref{fig:evoln}, a few show clear signs of the
CQV phenomenon in one sector, and marginal or non-existence signs in the
other.  While there is subjectivity in this assessment, to our
eyes cases for which at least one sector would be flagged as
``ambiguous'' include
TIC~368129164 (Sector 23 might be labeled an EB),
TIC~177309964 (Sector 38 would be simply a rotating star),
TIC~404144841 (Sector 38 looks like a rotating star),
TIC~201898222 (Sector 3 looks like a rotating star),
TIC~144486786 (Sector 32 might be an RS CVn),
and
TIC~38820496 (Sector 28 might be an RS CVn).
TIC~193831684, assessed on a single-sector basis, would probably be
labeled an eclipsing binary---in fact, \citet{2021ApJ...912..123J}
implicitly have already given this source such a label.  However,
based on the the shape evolution between Sectors 13 and 39, it is a
CQV.  One could easily also imagine in cases like TIC~206544316 that
if observed at lower signal to noise, the drastic shape evolution
would not be appreciated.  We emphasize that the periods themselves
were all stable to $<$0.1\%.  Broadly speaking, this shape evolution
suggests that CQVs have an ``on/off'' duty cycle of $\approx$75\%.
This type of correction is likely worth including in population-level
estimates of how intrinsically common CQVs are in the low-mass stellar
population \citep[e.g.][]{2022AJ....163..144G}.

\begin{figure*}[!tp]
	\begin{center}
		\centering
		\includegraphics[width=\textwidth]{f3.pdf}
		\vspace{-0.6cm}
		\caption{
		{\bf CQVs keep their periods but change their shapes.}
      32 of our \ngoods\ CQVs from Figure~\ref{fig:cqvs} had
      120-second cadence TESS data available for a baseline of at
      least two years; the 27 brightest are shown here.  Each panel
      shows one sector of TESS data, and is phased to its deepest
      minimum in flux.  Each panel's title shows the TIC identifier
      and approximate period in hours.  Text insets show the TESS
      sector numbers, which generally span two years, or at least
      1{,}000 cycles.  The vertical scale is fixed across sectors to
      clarify shape changes.
      Gray circles are raw 2-minute data; colored circles bin to 300
      points per cycle. 
		}
		\label{fig:evoln}
	\end{center}
\end{figure*}

@@

\begin{figure*}[!tp]
	\begin{center}
		\centering
		\includegraphics[width=0.98\textwidth]{f4.pdf}
		\vspace{-0.35cm}
		\caption{
      {\bf LP 12-502 (TIC~402980664) light curve}, where each time
      chunk represents one TESS orbit.  Data were acquired in Sectors
      18-19, 25-26, 53, and 57-58.  Flares are drawn in gray.  The red
      vertical lines highlight apparently instantaneous state changes
      in the shape of the dip pattern.  The light curve is binned to
      15-minute intervals so that there are 96 points per day, and each
      point is connected by a line.  
      Data gaps longer than one missing 15-minute are not
      interpolated; if data are missing, nothing is plotted.
		}
		\label{fig:lplc}
	\end{center}
\end{figure*}

\begin{figure*}[!t]
	\begin{center}
		\centering
		\includegraphics[width=\textwidth]{f5.pdf}
		\vspace{-0.6cm}
		\caption{
      {\bf Evolution of LP 12-502} ($P$=18.6\,h) at fixed period and
      epoch over three years.  Each panel shows one (stacked) TESS
      orbit; small text denotes relative cycle number.  There are 200
      binned black points per cycle.  The TESS pointing law dictates
      time gaps; larger gaps tend to yield larger shape changes.  The
      dips usually evolve over tens to hundreds of cycles.  However
      cycles 1233-1264 show a dip that ``switched'' from a depth and
      duration of 3\% and 3\,hr to 0.3\% and 1\,hr over less than one
      cycle (cf.~Figure~\ref{fig:lplc}).
		}
		\label{fig:lp}
	\end{center}
\end{figure*}

@@

\subsection{Mass flux estimate}
\label{subsec:massflux}

@@

In this work, we searched 120-second cadence TESS data collected
between July~2018 and Sep~2022 for complex quasiperiodic variables
(CQVs).  Our search sample included \nstarssearched\ K- and M-dwarfs
within 150\,pc, and was $\gtrsim 80\%$ complete within 30\,pc, and
$\lesssim 10\%$ complete at distances exceeding 100\,pc.

@@

Analyzing the TESS light curves and stellar properties of this sample
of objects, we draw the following conclusions.

\begin{enumerate}
	%
  \item CQVs are {\it quasi}periodic.  While the mean periods in our
    sample remain fixed over the baseline of available
    observations, the light curve shapes always evolve over timescales
    of thousands of cycles (Figure~\ref{fig:evoln}).
  %
  \item The same CQV can show dips with similar but clearly
    distinct periods.  LP 12-502, for instance, showed dips with four
    distinct periods within $\pm 0.3\%$ of its fundamental period,
    sometimes simultaneously, and each lasting for up to 50 cycles
    (Figure~\ref{fig:lpriver0}).
  %
    \item CQVs evolve over timescales that are both secular
    ($>$100\,cycles) and impulsive ($<$1 cycle).  ``State-switches''
    can cause dips to collapse instantaneously, and are often (but not
    exclusively) linked with observed optical flares.  Dip growth
    however seems to happen over durations of at least ten cycles, and
    slow dip decay also happens.
  %
    \item The rate of dip evolution can be used to place a model-dependent
    constraint on amount of material that is either being accreted or ejected
    during the state changes (Section~\ref{subsec:massflux}).
    Order of magnitude estimates require at least an asteroid belt's worth
    of dust ($10^{-4}$\,$M_\oplus$) over $10^8$ years, or 100 times more 
    material if the occulting matter is gas.
  %
    \item The CQV phenomenon persists for $\gtrsim$150\,Myr, based on
    the existence of multiple CQVs in AB Dor, the Pleiades, and
    Psc-Eri (Section~\ref{subsec:starprops}).  It may extend to even
    older ages, however the lack of detected CQVs in the Hyades and
    Praesepe suggests that the lifetime of the phenomenon may be
    limited to the first few hundred million years.
	%
    \item The duty cycle for CQVs seems to be $\approx 75$\%, based on
    the fraction of bonafide CQVs that turned on or turned off during
    TESS re-observations, two years after their initial observation.
  %
    \item Observed CQVs span a stellar mass range of 0.1-0.8\,M$_\odot$
    (Section~\ref{subsec:extreme}).
  %
    \item The closest CQVs to the Sun are at distances of 15-20\,pc, and
    the brightest CQVs have $V$$\approx$12 ($J$$\approx$7.5).  This
    conclusion is an extrapolation from the CQV sample derived in this work
    being $\gtrsim$80\% complete within 20\,pc.  Expanding our analysis of
    the TESS data to the full frame images would yield a truly
    volume-limited selection function, and would expand the CQV census
    by about a factor of two within 50\,pc, and by a factor of ten
    within 100\,pc.
\end{enumerate}

While many questions remain, two in particular will be 
important for clarifying what these objects might teach us in a
broader astrophysical context: {\it 1)} Is the eclipsing material
responsible for the phenomenon gas or dust?  {\it 2)} What sets
the characteristic clumping size for the circumstellar material?

The distinction between gas or dust is important because it will
clarify whether the CQV phenomenon is intrinsic, so that the material
comes from the star, or extrinsic, so that it is sourced through some
generic evolutionary phase of circumstellar disks.  This knowledge would in
turn propagate to our understanding of whether observing the
phenomenon is primarily teaching us about e.g.~dust production and
processing in circumstellar disks, or whether it is teaching us about
the ability of cold gas to remain stable in hot stellar coronae for
long durations.
Observationally, acquisition of medium- or high-resolution time-series
spectroscopy holds the best chance at resolving the gas vs.~dust
question.  Given the observed evolutionary timescales, such data
should be acquired simultaneously with photometric time-series
observations to help clarify its interpretation.

In both the gas and dust scenarios, CQVs are preferentially viewed
edge-on.
This implies that after correcting for the line-of-sight inclination,
it seems plausible that a sizable fraction of low mass stars (at
least one third; \citealt{2022AJ....163..144G}) trap circumstellar
material but are not observed in transit.
In addition, CQVs should preferentially show edge-on
transiting planets, at larger distances from the star than the
corotating material.
Given the interest level inherent to both of these points, important follow-up
observational work also includes searching for outer transiting
planets, and also measuring equatorial velocities in
order to test whether the stellar inclination angles are indeed
preferentially edge-on.

On the theoretical front,
building a physical understanding what sets the characteristic size
scale of the clumping material would help clarify the nature of
the magnetic and plasma environments around these young stars, 
and would also help build intuition for why the light curves have the
bizarre shapes that are observed.
It is certainly possible that the relevant puzzles in plasma physics
and radiative transfer could also be connected to our
understanding of the close-in rocky planets that are expected to be
present around most of these stars.
The challenges intrinsic to both the observational and theoretical
work seem worth the effort.

\acknowledgments
This work was supported by the 
Heising-Simons 51~Pegasi~b Fellowship (LGB).
TIC 402980664 was observed at 120-second cadence thanks to the TESS Guest
Investigator programs G022252 (PI: J.~Schlieder; Sectors 18, 19, 25,
26) and G04168 (PI: R.~Jayaraman; Sector 53).
While many conversations helped encourage this work,
a few thank-yous in particular (from LGB) 
are owed to G.~Laughlin, A.~Mann, L.~Rebull, and J.~Spake for clarifications and ideas.

{\bf DRAFT AUTHOR CONTRIBUTION STATEMENTS -- PLEASE REVISE IF 
	APPROPRIATE)}
LGB~and RJ conceived the project and executed the
dip-based and Fourier-based searches, respectively.
LGB~drafted the initial manuscript, and performed the cluster
membership, SED, and variability analyses.
SR and RJ vetted the results from the Fourier search.
LAH advised on project scope and experiment design.
G\'AB acquired and maintained the servers used to run the dip-finding
pipeline.
GRR is an architect of the TESS mission.
All authors assisted in manuscript revision.
